### 2021-12-10 thesis/tex/ICintro.tex
update

\section{Neutrino detection}
%TODO: Write down detection process. This section should be written carefully. 
% Specify the guys going into NC and CC. 
% First line only true for CC
% In next lines ,detail the detection process (interaction with detector matter osv). 
% Specify which are occurring in tracks and cascades.
We always observe neutrinos indirectly through their associated charged lepton. 
Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
via the $Z$), a charged lepton exits with altered properties. The lepton is then detected, and the properties of the neutrino involved in the 
interaction are then deduced. This deduction will be imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}.

In this work, we only study the detectors handled by the IceCube collaboration. They are of Cherenkov type, which means that they detect 
the secondary charged lepton by its emitted Cherenkov light, produced from its travel through the Antarctic ice. 
To detect the Cherenkov light, 60 Digital Optical Modules (DOMs) are placed on a long string up to \SI{17}{\metre} apart. 86 of these strings are then lowered
into \SI{2.5}{\km} deep boreholes in the ice. The holes are then sealed by refreezing the ice, resulting in a total of 5160 DOMs in a volume of approximately \SI{1}{\km^3}~\cite{weaverThesis}.

@@

\subsection{Atmospheric Neutrino Flux}
Atmospheric neutrinos originate from cosmic rays composed of high-energy protons interacting with nuclei in the atmosphere.
These interactions ultimately produces pions, which decay as 
\begin{align}\label{eq:pion} %Incorrect. Add muon decays
    &\pi^+ \to \mu^+ + \nm\,, \quad \pi^- \to \mu^- + \anm \nonumber \\
    &\pi^+ \to e^+ + \ne\,,\,\, \quad \pi^- \to e^- + \ane\,.
\end{align}
In the muonic decay channel, muons are emitted which will be detected by the IceCube detector.

The flux is provided in \cite{hondaData,hondaArticle}, and a selection is shown in Table~\ref{table:flux}.
The flux data is binned in $\cos(\theta_z)$. The fluxes are averaged over the azimuthal direction and solar minimum/maximum. 
The units of the fluxes are given as \si{\per\GeV \per\metre\squared \per\second \per\steradian} and are omitted
from the table for clarity. 
We note that the fluxes for $\nt$ and $\bar{\nu}_{\tau}$ are missing. Kaons do not decay into $\nt$. Thus, we never have to use probabilities in the form 
$P_{\tau \beta}$, since we have no starting atmospheric $\nu_\tau$ flux. 
Interpolating the data yields makes us capable of approximating all four necessary fluxes for a given true energy and true zenith.
The result of $\phi_\mu$ is shown in Fig.~\ref{fig:flux}. We see that the flux is almost entirely zenith independent. This is due to the 
very small cross-section of the neutrinos. For particles interacting through the electromagnetic interaction, we would expect to see a 
large difference between the flux of particles traversing through the whole diameter of the Earth, compared to particles that only penetrate a 
small rim of the crust. Here, however, the flux at the South Pole is almost the same! This does not mean that the oscillation probability will be 
equal. First, the difference in the density profiles introduces wildly different matter effects. 
Secondly, the zenith angle determines the baseline. Completely down-going neutrinos, with $\cos(\theta_z) = 0$ will be produced at an average distance of \SI{15}{\km}
overhead, travel down to the icy sheet of Antarctica, and then penetrate the ice down \SI{2}{\km} to the DOMs~\cite{hondapaper}. 
The energy dependence of the flux is approximately $E^{-2.7}$, so our expected event count at higher energies will suffer from this strong decline in flux.

@@

\subsection{True and Recontstructed Parameters}
After an event has occurred, the IceCube collaboration \emph{reconstruct} the event. 
This means that, given the parameters recorded by the detector, what are their `true' values?
We are interested in two variables: energy and direction. Each event is tagged with a probable energy and zenith angle, 
called the reconstructed parameters $\Ereco$ and $\zreco$, which are the parameters according to the DOMs.
In other words, the collaboration uses the recorded data to backtrack the event, using the reconstructed parameters to approximate the true parameters. 
So a charged lepton hits the DOMs, and we ultimately end up with the associated neutrino's true energy and zenith angle, $\Etrue$ and $\ztrue$. 
The reconstructed parameters are what we are using to analyze the data (because this is what the detector sees), while the true parameters are used in the 
determination of that neutrino's `actual' flux and cross-section (because this is what Nature sees).

@@

% \bibliographystyle{nature}
% \bibliography{ref.bib}
% \end{document}

>>>>

\section{Neutrino detection}
We always observe neutrinos indirectly through their associated charged lepton. 
Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
via the $Z$), a charged lepton exits with altered properties. The lepton is then detected, and the properties of the neutrino involved in the 
interaction are then deduced. This deduction will be imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}. 
% TODO: Write down CC NC equations after 1st paragraph, using N and N’ (N’ can be shower etc).
In this work, we only study the detectors handled by the IceCube collaboration. They are of Cherenkov type, which means that they detect 
the secondary charged lepton by its emitted Cherenkov light, produced from its travel through the Antarctic ice. 
To detect the Cherenkov light, 60 Digital Optical Modules (DOMs) are placed on a long string up to \SI{17}{\metre} apart. 86 of these strings are then lowered
into \SI{2.5}{\km} deep boreholes in the ice. The holes are then sealed by refreezing the ice, resulting in a total of 5160 DOMs in a volume of approximately \SI{1}{\km^3}~\cite{weaverThesis}.

@@

\subsection{Atmospheric Neutrino Flux}
Atmospheric neutrinos originate from cosmic rays composed of high-energy protons interacting with nuclei in the atmosphere.
These interactions ultimately produces pions, which decay as 
\begin{align}\label{eq:pion} %TODO: Incorrect. Add muon decays
    &\pi^+ \to \mu^+ + \nm\,, \quad \pi^- \to \mu^- + \anm \nonumber \\
    &\pi^+ \to e^+ + \ne\,,\,\, \quad \pi^- \to e^- + \ane\,.
\end{align}
In the muonic decay channel, muons are emitted which will be detected by the IceCube detector.

The flux is provided in \cite{hondaData,hondaArticle}, and a selection is shown in Table~\ref{table:flux}.
The flux data is binned in $\cos(\theta_z)$. The fluxes are averaged over the azimuthal direction and solar minimum/maximum. 
The units of the fluxes are given as \si{\per\GeV \per\metre\squared \per\second \per\steradian} and are omitted
from the table for clarity. 
We note that the fluxes for $\nt$ and $\bar{\nu}_{\tau}$ are missing. Kaons do not decay into $\nt$. Thus, we never have to use probabilities in the form 
$P_{\tau \beta}$, since we have no starting atmospheric $\nu_\tau$ flux. 
Interpolating the data yields makes us capable of approximating all four necessary fluxes for a given true energy and true zenith.
The result of $\phi_\mu$ is shown in Fig.~\ref{fig:flux}. We see that the flux is almost entirely zenith independent. 
% This is due to the 
% very small cross-section of the neutrinos. For particles interacting through the electromagnetic interaction, we would expect to see a 
% large difference between the flux of particles traversing through the whole diameter of the Earth, compared to particles that only penetrate a 
% small rim of the crust. Here, however, the flux at the South Pole is almost the same! This does not mean that the oscillation probability will be 
% equal. 
% First, the difference in the density profiles introduces wildly different matter effects. 
% Secondly, the zenith angle determines the baseline. Completely down-going neutrinos, with $\cos(\theta_z) = 0$ will be produced at an average distance of \SI{15}{\km}
% overhead, travel down to the icy sheet of Antarctica, and then penetrate the ice down \SI{2}{\km} to the DOMs~\cite{hondapaper}. 
The energy dependence of the flux is approximately $E^{-2.7}$, so our expected event count at higher energies will suffer from this strong decline in flux.

@@

\subsection{True and Reconstructed Parameters}
After an event has occurred, the IceCube collaboration \emph{reconstruct} the event. 
This means that, given the parameters recorded by the detector, what are their `true' values?
We are interested in two variables: energy and direction. Each event is tagged with a probable energy and zenith angle, 
called the reconstructed parameters $\Ereco$ and $\zreco$, which are the parameters according to the DOMs.
In other words, the collaboration uses the recorded data to backtrack the event, using the reconstructed parameters to approximate the true parameters. 
So a charged lepton hits the DOMs, and we ultimately end up with the associated neutrino's true energy and zenith angle, $\Etrue$ and $\ztrue$. 
The reconstructed parameters are what we are using to analyze the data (because this is what the detector sees), while the true parameters are used in the 
determination of that neutrino's `actual' flux and cross-section (because this is what Nature sees).

@@

### 2021-12-10 thesis/tex/nsiResults.tex
update

\section{Constraining the NSI parameters}\label{sec:constraining}
In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$ by considering the detectors separately as well as jointly.
For our analyses, we define our $\chi^2$ as
\begin{align}\label{eq:chisq_NSI}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory in bin $\{i,j,k\}$, where $i$ denotes the $\Ereco$ bin, $j$ denotes the $\zreco$ bin,
and $k$ denotes the event-type bin, i.e. track or cascade. 
$N_{ijk}^\text{data}$ is the observed number of events in that bin. $\sigma^\text{data}_{ijk}$ is the experimental uncertainty, and $\sigma^\text{syst}_{ijk}$ the uncorrelated systematic
incertainty.

@@

Comparing the PINGU and the DeepCore results in Fig.~\ref{fig:3D_NO}, we note that the best-fit for each NSI parameter for the PINGU experiment is expected to be zero. This is because the `data' we generated during 
the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU
since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.

\begin{figure}
   \begin{center}
      \includegraphics[scale = 0.7]{figures/joint_3D_NO.pdf}
      \caption{Confidence regions for PINGU and DeepCore scenarios listed in Table~\ref{table:syst_errors}, with their joint $\Delta \chi^2$ in maroon. $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
      parameters not shown in each panel are fixed to zero. 
      IceCube tracks only reveal $\emt$, and are displayed separately in Fig.~\ref{fig:IC_3D}. Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:3D_NO}
   \end{center}
\end{figure} 
\begin{figure}
   \begin{center} 
      \includegraphics[width=0.8\textwidth]{figures/PID_3D_emt.pdf}
      \caption{IceCube $\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
    $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters other than $\emt$ are fixed to zero.Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:IC_3D}
   \end{center}
\end{figure}

@@

%TODO: compare results

@@

 \begin{figure}[t]
   \begin{center}
      \begin{subfigure}{0.38\textwidth}
         \includegraphics[width=1\linewidth]{figures/PINGU_event_pulls.pdf}
         \caption{PINGU}\label{fig:PINGU_event_pulls}
      \end{subfigure}
      \begin{subfigure}{0.4\textwidth}
         \includegraphics[width=1\linewidth]{figures/DC_event_pulls.pdf}
         \caption{DeepCore}\label{fig:DC_event_pulls}
      \end{subfigure}
    \end{center}
   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years.}
\end{figure}%TODO: redo these with same emt as flux_ratio? keep this, but align them better

There is no reason for us to assume that only one NSI parameter exists in Nature, unless we impose a symmetry on the gauge group which generates NSI. For example, the matter potential matrix in our Hamiltonian from Eq.~\eqref{eq:V_matrix} is diagonal since the interaction Lagrangian respects lepton number conservation. 
The PMNS matrix, on the other hand, has off-diagonal elements because the kinetic Lagrangian breaks this symmetry. So ideally, we would simulate a grid where all NSI parameters are allowed to vary, 
but this is not feasible. Thus, we take we set $\ett = 0$ and let $\emt,\eem,\eet$ vary, along with $\dm[31]$ and $\theta_{23}$. We let $\ett=0$ because we saw that it did not influence the other parameters. 
We then marginalize out the standard oscillation parameters and one of the NSI parameters and plot the remaining two in Fig.~\ref{fig:PINGU_2D}. We see that the pairs $\eem - \emt$ and $\eet - \emt$ are symmetrical. 
Hence, we can see that no relationship exists between them. With $\eet - \eem$, however, the contours are assuming a different shape. The contour allows positive values of $\eet$ and $\eem$ to a greater degree than mixed or negative values.

>>>>

\section{Constraining the NSI parameters}\label{sec:constraining}
%TODO Ch 5.2 write what new things we have in the sterile analysis/chi2. Ie that NSI is showing in GeV -> deep core 
In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$ by considering the detectors separately as well as jointly.
For our analyses, we define our $\chi^2$ as
\begin{align}\label{eq:chisq_NSI}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory in bin $\{i,j,k\}$, where $i$ denotes the $\Ereco$ bin, $j$ denotes the $\zreco$ bin,
and $k$ denotes the event-type bin, i.e. track or cascade. 
$N_{ijk}^\text{data}$ is the observed number of events in that bin. $\sigma^\text{data}_{ijk}$ is the experimental uncertainty, and $\sigma^\text{syst}_{ijk}$ the uncorrelated systematic
incertainty.

@@

Comparing the PINGU and the DeepCore results in Fig.~\ref{fig:3D_NO}, we note that the best-fit for each NSI parameter for the PINGU experiment is expected to be zero. This is because the `data' we generated during 
the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU
since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
% TODO: Write a few lines about the plots 5.4 and 5.5
\begin{figure}
   \begin{center}
      \includegraphics[scale = 0.7]{figures/joint_3D_NO.pdf}
      \caption{Confidence regions for PINGU and DeepCore scenarios listed in Table~\ref{table:syst_errors}, with their joint $\Delta \chi^2$ in maroon. $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
      parameters not shown in each panel are fixed to zero. 
      IceCube tracks only reveal $\emt$, and are displayed separately in Fig.~\ref{fig:IC_3D}. Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:3D_NO}
   \end{center}
\end{figure} 
\begin{figure}
   \begin{center} 
      \includegraphics[width=0.8\textwidth]{figures/PID_3D_emt.pdf}
      \caption{IceCube $\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
    $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters other than $\emt$ are fixed to zero.Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:IC_3D}
   \end{center}
\end{figure}

@@

%TODO: compare results, fix tables

@@

 \begin{figure}[t]
   \begin{center}
      \begin{subfigure}{0.38\textwidth}
         \includegraphics[width=1\linewidth]{figures/PINGU_event_pulls.pdf}
         \caption{PINGU}\label{fig:PINGU_event_pulls}
      \end{subfigure}
      \begin{subfigure}{0.4\textwidth}
         \includegraphics[width=1\linewidth]{figures/DC_event_pulls.pdf}
         \caption{DeepCore}\label{fig:DC_event_pulls}
      \end{subfigure}
    \end{center}
   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years.}
\end{figure}
%TODO 5.6 is small, fix labels
%TODO:  Write from fig 5.7 that let Eem are anti-correlated, while no significant correlation can be seen from emt-emt, emt-eet.
There is no reason for us to assume that only one NSI parameter exists in Nature, unless we impose a symmetry on the gauge group which generates NSI. For example, the matter potential matrix in our Hamiltonian from Eq.~\eqref{eq:V_matrix} is diagonal since the interaction Lagrangian respects lepton number conservation. 
The PMNS matrix, on the other hand, has off-diagonal elements because the kinetic Lagrangian breaks this symmetry. So ideally, we would simulate a grid where all NSI parameters are allowed to vary, 
but this is not feasible. Thus, we take we set $\ett = 0$ and let $\emt,\eem,\eet$ vary, along with $\dm[31]$ and $\theta_{23}$. We let $\ett=0$ because we saw that it did not influence the other parameters. 
We then marginalize out the standard oscillation parameters and one of the NSI parameters and plot the remaining two in Fig.~\ref{fig:PINGU_2D}. We see that the pairs $\eem - \emt$ and $\eet - \emt$ are symmetrical. 
Hence, we can see that no relationship exists between them. With $\eet - \eem$, however, the contours are assuming a different shape. The contour allows positive values of $\eet$ and $\eem$ to a greater degree than mixed or negative values.

### 2021-12-10 thesis/tex/nsiTheory.tex
update

By combining oscillation data and neutrino-nucleon scattering at the COHERENT experiment, 90 \% CL ranges of some of 
the NSI parameters were constrained in~\cite{coherent} to
\begin{align}\label{eq:coherentbounds}
    -0.090 < &\ett < 0.38 \nonumber \\
    -0.01 < &\emt < 0.009 \nonumber \\
    -0.073 < &\eem < 0.044 \nonumber \\
    -0.15 < &\eet < 0.13\,.
\end{align}

% we are free to do since any multiple added or subtracted from diagonal does not affect the eigenvectors of the Hamiltonian and thus not the
% probabilities. So jusb t as we subtracted away $V_{NC}$ back in Eq.~\ref{eq:components}, we can subtract $\emm$ and rotate it away.
% Our NSI potential matrix now takes the form 
% {µmmb m  m mb  mb  mbb  mb bmMoreover, it is common to subtract $\emm$ from the diagonal, which
% \begin{align} m mmb
%     \begin{pmatrix}
%         \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
%         \epsilon_{e \mu} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
%         \epsilon_{e\tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau}
%     \end{pmatrix} 
%     - \epsilon_{\mu\mu}
%     \begin{pmatrix}
%         1 & 0 & 0 \\
%         0 & 1 & 0 \\
%         0 & 0 & 1 
%     \end{pmatrix}
%      &= \begin{pmatrix}
%         \epsilon_{ee}- \epsilon_{\mu\mu} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
%         \epsilon_{e \mu} & 0 & \epsilon_{\mu\tau}  \\
%         \epsilon_{e\tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau} - \epsilon_{\mu\mu}
%     \end{pmatrix} \nonumber \\
%     &= \begin{pmatrix}
%         \epsilon_{ee}- \epsilon_{\mu\mu} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
%         \epsilon_{e \mu} & 0 & \epsilon_{\mu\tau}  \\
%         \epsilon_{e\tau} & \epsilon_{\mu\tau} & \ep
%     \end{pmatrix}\,,
% \end{align}
% where $\ep = \ett - \emm$.

@@

Since all standard matter potentials are diagonal, 
the elements $\epsilon_{\a\b},\, \a = \b$ will directly adjust the matter potential felt 
by flavor $\a$. The off-diagonal terms have a more interesting theoretical implication as they open up matter interactions across flavors. Remember, in the Standard model,
we are restricted to weak interactions that conserve lepton number. However, an off-diagonal NSI parameter allows flavor transitions during matter interactions. Thus,
the off-diagonal elements constitute new sources of flavor violation.
Moreover, $\epsilon_{\a\b}$ modifies the $\nu_\a \to \nu_\b$ transition independently
of the mixing matrix. Thus, we can in theory boost a flavor transition that is suppressed by the mixing matrix. Moreover, since we have 6 NSI parameters, and the PMNS
matrix is parametrized with only 3 parameters, we have more degrees of freedom when adjusting the probabilities using the NSI matrix. Each term in the PMNS matrix consists of at least
two of the three mixing angles, making them much more dependent on each other.

@@

Moving on to $\eem$ and Fig.~\ref{fig:eem_eet_probs}, we see that both probabilities has shifted downwards for $\Etrue > \SI{500}{\GeV}$.
In Fig.~\ref{fig:eem_eet_probs}, we see that the muon channel remains largely unaffected of the value of $\eet$ as we expected. The expection of this lies 
in the DeepCore region of rapid oscillations, where mixing is more violent. 
\begin{figure}
    \begin{center}%TODO subplots and fix labels in parahgraph aboveto match them
        \includegraphics[width=0.9\textwidth]{figures/emt_probs.pdf}
        \includegraphics[width=0.9\textwidth]{figures/ett_probs.pdf}
        \caption{\emph{Top panel:} Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\emt = 0.02$. All other NSI parameters are fixed to zero. In the \si{\GeV} range, $\emt$ shifts the oscillations to the right for $\nm$, and to the left for $\anm$. At \si{\TeV} energies, both probabilites simply get shifted down, resulting in a net reduction of track events.
        \emph{Bottom panel:} Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\ett = 0.05$. All other NSI parameters are fixed to zero. $\ett$ does not affect the probabilities above \SI{100}{\GeV} and this parameter is thus unable to be constrained by tracks in IceCube in our study. However, the dampening of the $\anm$ survival probability will be visible to DeepCore and PINGU, since it occurs within their energy ranges.}
        \label{fig:emt_ett_probs}
    \end{center}
\end{figure}

>>>>

By combining oscillation data and neutrino-nucleon scattering at the COHERENT experiment, 90 \% CL ranges of some of 
the NSI parameters were constrained in~\cite{coherent} to
\begin{align}\label{eq:coherentbounds}
    -0.090 < &\,\ett < 0.38 \nonumber \\
    -0.01 < &\,\emt < 0.009 \nonumber \\
    -0.073 < &\,\eem < 0.044 \nonumber \\
    -0.15 < &\,\eet < 0.13\,.
\end{align}

@@

Since all standard matter potentials are diagonal, 
the elements $\epsilon_{\a\b},\, \a = \b$ will directly adjust the matter potential felt 
by flavor $\a$. The off-diagonal terms have a more interesting theoretical implication as they open up matter interactions across flavors. Remember, in the Standard model,
we are restricted to weak interactions that conserve lepton flavor. However, an off-diagonal NSI parameter allows flavor transitions during matter interactions. Thus,
the off-diagonal elements constitute new sources of flavor violation.
Moreover, $\epsilon_{\a\b}$ modifies the $\nu_\a \to \nu_\b$ transition independently
of the mixing matrix. Thus, we are not confined to the parameters of the mixing matrix: now we have introduced the 
possibility of additional interactions that can cause the flavor change. Moreover, since we have 6 NSI parameters, and the PMNS
matrix is parametrized with only 3 parameters, we have more degrees of freedom when adjusting the probabilities using the NSI matrix. Each term in the PMNS matrix consists of at least
two of the three mixing angles, making them much more dependent on each other.

@@

Moving on to $\eem$ and Fig.~\ref{fig:eem_eet_probs}, we see that both probabilities has shifted downwards for $\Etrue > \SI{500}{\GeV}$.
In Fig.~\ref{fig:eem_eet_probs}, we see that the muon channel remains largely unaffected of the value of $\eet$ as we expected. The expection of this lies 
in the DeepCore region of rapid oscillations, where mixing is more violent. 
\begin{figure}
    \begin{center}%TODO subplots and fix labels in parahgraph aboveto match them
        \includegraphics[width=0.99\textwidth]{figures/emt_probs.pdf}
        \includegraphics[width=0.99\textwidth]{figures/ett_probs.pdf}
        \caption{\emph{Top panel:} Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\emt = 0.02$. All other NSI parameters are fixed to zero. In the \si{\GeV} range, $\emt$ shifts the oscillations to the right for $\nm$, and to the left for $\anm$. At \si{\TeV} energies, both probabilites simply get shifted down, resulting in a net reduction of track events.
        \emph{Bottom panel:} Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\ett = 0.05$. All other NSI parameters are fixed to zero. $\ett$ does not affect the probabilities above \SI{100}{\GeV} and this parameter is thus unable to be constrained by tracks in IceCube in our study. However, the dampening of the $\anm$ survival probability will be visible to DeepCore and PINGU, since it occurs within their energy ranges.}
        \label{fig:emt_ett_probs}
    \end{center}
\end{figure}
